---
title: "sasproj"
author: "Poojaanjali Vasu"
date: "4/28/2020"
output: 
  html_document:   
    code_download: yes
    code_folding: hide
    fig_height: 6
    fig_width: 9
  word_document: default
runtime: shiny

---
<style type="text/css">

body, td {
   font-size: 12px;
}
code.r{
  font-size: 10px;
}
pre {
  font-size: 10px
}
h4.author { 
    font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: right;
}
</style>

# {.tabset .tabset-fade .tabset-pills}

## __Sudoko Platform__

### {.tabset .tabset-fade}

#### __Introduction__  

><font size="2">
This Statistical report presents  a clear overview of the Sudoko Analysis.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## __Manipulation of data__ 

### {.tabset .tabset-fade}

#### __Data Manipulation__ 

```{r,eval=FALSE}



library(tidyverse)
# library(multcomp)

setwd("/users/students/19251512/project/")

# sudoku<-read.csv("3SudokuCombined.csv",stringsAsFactors = F)

sudoku<-read.csv("3SudokuCombined.csv", header=T, na.strings=c("","NA"),stringsAsFactors = F)

sudoku<-as_tibble(sudoku)

#############################################################################
#############################################################################
#############################################################################
#######################****** Phase 1 ******#################################
#############################################################################
#############################################################################
#############################################################################

########### Data Cleaning (#before,type,correct,sec )###############################

glimpse(sudoku)


# Class to factor

sudoku$Class<-as.factor(sudoku$Class)

# Response=Correct to factor

sudoku$Correct<-factor(ifelse(sudoku$Correct=='Yes',1,0))


# Time2=total time in sec (change it to numeric)

sudoku$Time2<-suppressWarnings(as.numeric(sudoku$Time2))


# Imputation and cleaning

# 1. Cleaning Type

table(sudoku$Type)

sudoku$Type<-ifelse(sudoku$Type=="Letter","Letters",sudoku$Type)
sudoku$Type<-ifelse(sudoku$Type=="Number","Numbers",sudoku$Type)
sudoku$Type<-ifelse(sudoku$Type=="Symbol","Symbols",sudoku$Type)

sudoku$Type<-factor(sudoku$Type)


#2 Clening before2 i.e. inside3 and within_3 are same and out_3 and ouside
# are same


table(sudoku$Before2)


sudoku$Before2<-ifelse(sudoku$Before2=="Inside","Within_3",sudoku$Before2)
sudoku$Before2<-ifelse(sudoku$Before2=="Outside","Out_3",sudoku$Before2)


## Filling missing values of before1 using before2 details

sudoku%>%
  mutate(Before1=replace(Before1,
                         is.na(Before1)&!is.na(Before2)&Before2=='No',
                         'No')
  )->sudoku     

sudoku%>%
  mutate(Before1=replace(Before1,
                         is.na(Before1)&!is.na(Before2)&Before2!='No',
                         'Yes')
  )->sudoku 

sudoku$Before1<-factor(ifelse(sudoku$Before1=='Yes',1,0))

table(sudoku$Before1)


#### Checking if missing null values in Time2 can be filled using Time1:Min:Sec

sudoku%>%filter(is.na(Time2),!is.na(Time1),!is.na(Mins),!is.na(Seconds))

# As it returns zero rows so Time1,Mins and Seconds are worthless columns so dropping it.

# sudoku%>%select(-Time1,-Mins,-Seconds)->sudoku

sudoku%>%dplyr::select(-Time1,-Mins,-Seconds)->sudoku

glimpse(sudoku)


#checking if there is any column filled with value "."

lapply(sudoku,function(x)which((x==".")==T))

sudoku[c(1302,1304,1499,1533,1548),]

# We cannot impute anything for this . 


glimpse(sudoku)


# Trying to impute before2 using before1 , setting before2='No' if before1=0 

sudoku%>%
  mutate(Before2=replace(Before2,
                         is.na(Before2)&!is.na(Before1)&Before1==0,
                         'No')
  )->sudoku
# 
# sudoku%>%filter(is.na(Before2)&!is.na(Before1)&Before1==0)


sudoku%>%filter(is.na(Before2))%>%nrow *100 / nrow(sudoku)


# Since around 26% of data is missing even after imputing, 
# so we skip this column 


sudoku%>%filter(is.na(Logic))%>%nrow *100 / nrow(sudoku)


# Since around 34.86% of data is missing and we cannot impute this column,
# so we skip this column 


sudoku%>%dplyr::select(-6,-7)->sudoku


sudoku%>%filter(is.na(Time2))%>%nrow *100 / nrow(sudoku)


# Since around 6% of data is missing so we KEEP this column 


#############################################################################
#############################################################################
#############################################################################
#######################****** Phase 2 ******#################################
#############################################################################
#############################################################################
#############################################################################

# Variable Analysis
# 1. Categorical Data

ggplot(data=sudoku,aes(x=Correct))+geom_bar()+ggtitle("Distribution of Correct")

ggplot(data=sudoku,aes(x=Type,fill=Correct))+geom_bar(position = "fill")+
  ggtitle("The conditional distribution")

paste("Distribution of Sudoku Type")
sudoku%>%group_by(Type)%>%count()%>%mutate(Relative_Freq=n/nrow(sudoku)*100)%>%
  rename(Freq=n)


# 2. Continuous Data

sudoku%>%filter(Correct==1)%>%
  ggplot(data=.,aes(x=Time2))+
  geom_histogram(breaks=seq(0,max(sudoku$Time2,na.rm = T),by=50),colour='black')+
  scale_x_continuous(breaks=seq(0,max(sudoku$Time2,na.rm = T),by=100))+
  ggtitle("Histogram of Correctly Completely Sudoku")


sudoku%>%filter(Correct==1)%>%
  ggplot(data=.,aes(x=Type,y=Time2))+geom_boxplot()+
  ggtitle("Boxplot of Correctly Completely Sudoku's Time by Sudoku type")


sudoku%>%filter(Correct==1)%>%
  group_by(Type)%>%
  summarise(min=fivenum(Time2,na.rm = T)[1],
            Q1=fivenum(Time2,na.rm = T)[2],
            median=fivenum(Time2,na.rm = T)[3],
            Q3=fivenum(Time2,na.rm = T)[4],
            max=fivenum(Time2,na.rm = T)[5],
            mean=mean(Time2,na.rm = T),
            iQR=IQR(Time2,na.rm = T),
            SD=sd(Time2,na.rm = T))

# sudoku%>%filter(Time2==910)
# We are seeing outliers and need to highlight that


####### Chi sq test of independence

# correct vs type 
# Chi Sq test of independence to check if there is any dependency between 
# if sudoku was correct and sudoku type at 0.05 significant level

table(Type=sudoku$Type,Correct=sudoku$Correct) 

chisq.test(sudoku$Type,sudoku$Correct)

# pvalue<0.05, so there is evidence to prove that there exists dependency
# between correct and sudoku type, This can be noticable
# as we see that greek type has the lowest correct solutions

# correct vs experience
# Chi Sq test of independence to check if there is any dependency between 
# if sudoku was correct and sudoku experience at 0.05 significant level

table(Previous_Exp=sudoku$Before1,Correct=sudoku$Correct)

chisq.test(sudoku$Before1,sudoku$Correct)

# pvalue<0.05, so there is evidence to prove that there exists dependency
# between correct and before hand experience, This can be noticable
# as we see that those who played before got correct solutions more.


# correct vs class
# Chi Sq test of independence to check if there is any dependency between 
# if sudoku was correct and class at 0.05 significant level


table(Previous_Exp=sudoku$Class,Correct=sudoku$Correct)

chisq.test(sudoku$Class,sudoku$Correct)


# pvalue<0.05, so there is evidence to prove that there exists dependency
# between correct and sudoku class, This can be noticable
# as we see that those who played before got correct solutions more.


################################################################################
##T test (only on correct data i.e. Sudoku is correct)


correct_sudoku<-sudoku%>%filter(Correct==1)

# sudoku%>%lm(data=.,Time2~Type)%>%summary()


sudoku_known<-correct_sudoku%>%filter(Type!='Greek')
sudoku_unknown<-correct_sudoku%>%filter(Type=='Greek')


t.test(sudoku_known$Time2,sudoku_unknown$Time2)


# A Welch Two Sample t-test detected a significant difference(p<0.05) in mean time to succesfully complete
# between known letter and uunknown letter in sudoku(greek).

remove(sudoku_known)
remove(sudoku_unknown)


################################################################################
### One-way ANOVA (only on correct data i.e. Sudoku is correct)

fit<-aov(data=correct_sudoku,Time2~Type)

anova(fit)

# This states there was evidence of an effect of Sudoku type on the
# length of time to Sudoku completion

# TukeyHSD(fit)

remove(fit)
remove(correct_sudoku)
#############################################################################
#############################################################################
#############################################################################
#######################****** Phase 3 ******#################################
#############################################################################
#############################################################################
#############################################################################


# Analysis Starts
# library(epiDisplay)  

# Logistic Regression on all variable except Time2 as we will do different test for Time2

sudoku[-5]->sudoku_1

na.omit(sudoku_1)->sudoku_1


# Model Building and validations

before  <-glm(Correct~Before1,data = sudoku_1,family="binomial")
type    <-glm(Correct~Type    ,data = sudoku_1,family="binomial")
class   <-glm(Correct~Class,data = sudoku_1,family="binomial")

before_type  <-glm(Correct~Before1+Type,data = sudoku_1,family="binomial")
type_class    <-glm(Correct~Type+Class,data = sudoku_1,family="binomial")
class_before  <-glm(Correct~Class+Before1,data = sudoku_1,family="binomial")

full<-glm(Correct~Before1+Type+Class,data = sudoku_1,family="binomial")

intersect_model<-glm(Correct~Before1*Type*Class,data = sudoku_1,family="binomial")

intercept<-glm(Correct~1,data = sudoku_1,family="binomial")

# Model Bulding and variable significance testing

# Hypothesis 1 : 
# H0 : Intersection is not significant (Reduced model is better)
# H1 : Intersection is significant (full model is better)

anova(full,intersect_model, test = "LR")


# This states Intersection is not significant and thus go with a reduced model(full)
# -----------------------------------------------------------------

# Hypothesis 2 : 
# H0 : Class is not significant (Reduced model is better)
# H1 : Class is significant (full model is better)

anova(before_type,full, test = "LR")


# This states class is not significant and thus go with a reduced model
# -----------------------------------------------------------------
# Hypothesis 3 : 
# H0 : Type is not significant (Reduced model is better)
# H1 : Type is significant (full model is better)

anova(before,before_type, test = "LRT")

# This states Type is significant and thus go with a full model

# ------------------------------------------------------------------
# Hypothesis 4 : 
# H0 : Before1  is not significant (Reduced model is better)
# H1 : Before1  is significant (full model is better)

anova(type,before_type, test = "LRT")

# This states Before1 is significant and thus go with a full model
# ---------------------------------------------------------------------


#Interpretation  
summary(before_type)
exp(before_type$coefficients)

# 
# Hypothesis 1:
#   
#   The odds of successfully completing the Sudoku correctly were 9.81 times higher for 
# those who had played Sudoku before relative to those who had not played before
# 
# Hypothesis 2:
#   
#   The odds of successfully completing the Sudoku correctly were 1.79 times higher for 
# those who had played Sudoku of type "Letters" rather than "Greek",
# The odds of successfully completing the Sudoku correctly were 1.99 times higher for 
# those who had played Sudoku of type "Numbers" rather than "Greek",
# The odds of successfully completing the Sudoku correctly were 1.79 times higher for 
# those who had played Sudoku of type "Symbols" rather than "Greek",
# 
# Hypothesis 3:
#   
#   The class had no effect on successfully completing the sudoku puzzle so as 
# hypothesis 3 we will do survival analysis on Time2
# 




# Approach 2 of variable selection

require(MuMIn) 
model.sel(intercept,before,type,class,before_type,type_class,class_before,full,
          intersect_model) 


# This states as approach1 go with model having Before1 and Type  as it has lowest AIC.


# Approach 3 using StepAIC

library(MASS)
stepAIC(intersect_model,trace = T)$anova

# This also states go with model having Before1 and Type  as it has lowest AIC.



remove(before)
remove(type)
remove(class)
remove(type_class)
remove(class_before)
remove(full)
remove(intercept)
remove(intersect_model)
remove(sudoku_1)

# Accuracy of model is around 81%
table(sudoku$Correct,as.numeric(predict(before_type,newdata = sudoku
                                        ,type = "response")>0.5))


remove(before_type)

############# Survival Analysis on Time2

library(survival)
# install.packages("survminer")
library(survminer)
library(ggfortify)

# Event: 1-> sucesfuly completed
# 0-> not completed
# 
# Time2 is the survival time


sudoku[c(1,2,3,4,5)]%>%as.data.frame->sudoku_survival


fct_explicit_na(sudoku_survival$Before1)->sudoku_survival$Before1

as.character(sudoku_survival$Correct)%>%as.numeric->sudoku_survival$Correct

surv_object <- Surv(time = sudoku_survival$Time2,event = sudoku_survival$Correct)


fit1 <- survfit(surv_object ~ 1, data = sudoku_survival)

fit2 <- survfit(surv_object ~ Type, data = sudoku_survival)
# summary(fit2)


# res.sum <- surv_summary(fit2)

# res<-fortify(fit1)

# # Understanding Summary,
# time is nothing but time2 in ascending order
# n.risk is the the total no of person at risk of dying i.e those who didnt solved puzzle yet.
# n.event is the no of people that solved the event at time=time2
# survival is the no of people still alive in percentage

# https://rpkgs.datanovia.com/survminer/index.html

ggsurvplot(fit1, data = sudoku_survival, pval = T,conf.int = T,
           risk.table = F,censor.size=4,censor.shape="|")

ggsurvplot(fit2, data = sudoku_survival, pval = T,conf.int = T,
           risk.table = F,censor.size=7,censor.shape="|")

# 
# ggplot(data = res, aes(x = time, y = surv, color = strata)) +
#   geom_line() + 
#   # plot censor marks
#   geom_point(aes(shape = factor(ifelse(n.censor >= 1, 1, NA)))) + 
#   # format censor shape as "+"
#   scale_shape_manual(values = 3) + 
#   # hide censor legend 
#   guides(shape = "none") +ggtitle("Kaplan-Meier curves")


# ----------------------------------------

# Time entries on worksheets with incorrect solutions contain information on the 
# quantity of interest since they give LOWER bounds for true completion times.
# The continuous variable time is therefore referred to as right-censored.
# 
# In our context below terms indicates,
#   a. Survival -> Puzzle has not yet correctly completed.
#   b. Death    -> Puzzle has correcly completed.
#   c. Censor point -> TIme of a person who completed puzzle incorrectly.

# T -> Time of death(after correctly completing)
# 
# survival function given as, S(t) = P(T≥ t) for time t.
# 
# The survival function is a function that gives the probability that a patient,
# device, or other object of interest will survive beyond any specified time(here t).
# 
# Using this method, plot shows the estimated survival probabilities(y-axis)
# versus time (x-axis) for each Sudoku type. 
# Censored data points are indicated by a | symbol and the probability of
# completing the Sudoku puzzle correctly by time t is estimated by 1- E(S(t)) 
# (indicates estimated).

fit2

# From the fit1 function we can see correctly completing sudoku given the sudoku type
# is 125 seconds for Numbers, 149 seconds for Letters, 205 seconds for Symbols,
# while 246 seconds for Greek, these unbiased median
# estimates are all higher than the biased medians presented for
# the subset of correct Sudokus only
# 
# Hypothesis:
#   
#   Ho: There is no statistical difference in median survival time between 4 different
# types of sudoku puzzle
# 
# HA: This is statistical difference in median survival time between 4 different
# types of sudoku puzzle



library(coin)

logrank_test(surv_object~Type, data=sudoku_survival)


# From p value we can say accept alternate hypothesis and say 
# There is statistical difference in median survival time between 4 different
# types of sudoku puzzle
```


## __Sudoko Visualisation__ 

### {.tabset .tabset-fade}

#### __Visualisation__ 


```{r}
library(RCurl)
getURL('https://public.tableau.com/profile/jak94#!/vizhome/SudokuProjectTableauWorkbook/Viz1', ssl.verifyhost=FALSE, ssl.verifypeer=FALSE)

```

